---
output:
  github_document:
    html_preview: false
---

# iNZight Development Repository

This repository is where we can store all of our development scripts, files, bug lists, etc.

```{r,echo=FALSE,message=FALSE}
library(magrittr)
library(dplyr)

pkgs <- tibble(
  package = c(
    "iNZight", "iNZightPlots", "iNZightMR", "iNZightTools",
    "iNZightTS", "iNZightRegression", "iNZightModules",
    "iNZightMaps"
  )
) %>%
  mutate(
    master = glue::glue("![R-CMD-check](https://github.com/iNZightVIT/{package}/workflows/R-CMD-check/badge.svg)"),
    dev = glue::glue("![R-CMD-check](https://github.com/iNZightVIT/{package}/workflows/R-CMD-check/badge.svg?branch=dev)"),
    codecov = glue::glue("[![Codecov test coverage](https://codecov.io/gh/iNZightVIT/{package}/branch/master/graph/badge.svg)](https://codecov.io/gh/iNZightVIT/{package}?branch=master)"),
    cran = glue::glue("[![CRAN](https://www.r-pkg.org/badges/version/{package})](https://CRAN.R-project.org/package={package})")
  )

knitr::kable(pkgs)
```


***
## To start developing iNZightVIT (assumes Linux):

1) Create a new directory: `~/iNZight`
   (This must be in your home directory)
```{bash,eval=FALSE}
mkdir ~/iNZight
cd ~/iNZight
```

2) Inside `iNZight`, clone the `dev` repository (assumes git is set up):
```{bash,eval=FALSE}
git clone git@github.com:iNZightVIT/dev
cd dev
```

3) From inside the `dev` directory, build the full iNZight development directories:
```{bash,eval=FALSE}
make build
cd ..
```

4) Now, inside `~/iNZight/`, you will have all of the required directories for
   developing iNZight.

***
## Dependency Structure


This graph shows the interaction between various iNZight R packages.

```{r,echo=FALSE,message=FALSE,fig.width=8,fig.height=5}
library(magrittr)
library(ggraph)
library(igraph)

pkgs <- c(
  "iNZight", "iNZightPlots", "iNZightMR", "iNZightTools",
  "iNZightTS", "iNZightRegression", "iNZightModules",
  "iNZightMaps"
)
get_deps <- function(pkg, dep) {
  deps <- remotes::local_package_deps(pkg, dep)
  if (length(deps) == 0 || !any(deps %in% pkgs)) return(NULL)
  deps <- deps[deps %in% pkgs]

  tibble::tibble(
    package = rep(basename(pkg), length(deps)),
    dependency = deps,
    type = rep(dep, length(deps))
  )
}
pkg_deps <- lapply(pkgs,
  function(pkg) {
    dplyr::bind_rows(
      depends = get_deps(file.path("..", pkg), "Depends"),
      imports = get_deps(file.path("..", pkg), "Imports"),
      suggests = get_deps(file.path("..", pkg), "Suggests"),
      enhances = get_deps(file.path("..", pkg), "Enhances")
    )
  }
) %>% dplyr::bind_rows()

set.seed(27)
graph <- graph_from_data_frame(pkg_deps)
ggraph(graph, layout = "dh") +
  geom_edge_fan(
    aes(
      colour = type,
      alpha = type,
      start_cap = label_rect(node1.name, padding = margin(2, 2, 3, 2, "mm")),
      end_cap = label_rect(node2.name, padding = margin(2, 2, 3, 2, "mm"))
    ),
    arrow = arrow(length = unit(3, "mm"), type = "open")
  ) +
  geom_node_label(aes(label = name)) +
  theme_graph() +
  theme(legend.position = "bottom") +
  scale_edge_colour_manual(values = c("orangered", "steelblue")) +
  scale_edge_alpha_manual(values = c(1, 0.5)) +
  xlim(-6.5, 2)

```



***


If you have any issues with these instructions, please email `tom.elliott@auckland.ac.nz`.
